\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{listings}
\usepackage{xcolor}

\geometry{letterpaper, margin=1in}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    basicstyle=\ttfamily\footnotesize,
    breaklines=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    tabsize=2
}

\lstset{style=mystyle}

\title{\textbf{Editorial: Problem D - The Aquarium}}
\author{Setter: Hudson}
\date{}

\begin{document}

\maketitle

\section*{Problem Overview}
Partition an array of length $N$ into exactly $K$ subarrays to minimize:
$$ \sum_{i=1}^K ((len_i)^2 + sum_i) $$
where $len_i$ is the length and $sum_i$ is the sum of elements of the $i$-th subarray.

\section*{Difficulty Analysis}
Rating: \textbf{3000}.
Constraints: $N, K \le 10^5$.
Naive DP: $dp[k][i]$ is min cost to split prefix $i$ into $k$ parts. $O(N^2 K)$.
Optimized DP: Using Convex Hull Trick (CHT) reduces transition to $O(1)$ or $O(\log N)$, giving $O(NK)$. Still too slow.
The function $f(K) = \text{min total cost with exactly } K \text{ subarrays}$ is \textbf{convex}.
This allows the use of **WQS Binary Search** (Alien's Trick).

\section*{Solution Approach}
1. **Alien's Trick:**
   Instead of fixing $K$, we introduce a penalty $\lambda$ for starting a new subarray.
   We minimize: Total Cost $+ \lambda \times (\text{number of subarrays})$.
   For a fixed $\lambda$, let $g(\lambda)$ be the minimum cost and $cnt(\lambda)$ be the number of subarrays used.
   We can binary search for $\lambda$ such that $cnt(\lambda) \approx K$.
   The answer will be $g(\lambda) - \lambda \times K$.

2. **Inner DP Optimization:**
   With fixed $\lambda$, we just need to find the min cost for \textit{any} number of subarrays.
   $dp[i] = \min_{j < i} \{ dp[j] + (i - j)^2 + (S[i] - S[j]) + \lambda \}$
   where $S[x]$ is prefix sum of $A$.
   Expand terms:
   $dp[i] = i^2 + S[i] + \lambda + \min_{j < i} \{ dp[j] + j^2 - S[j] - 2ij \}$
   This is the form $y = mx + c$ where:
   $m = -2j$
   $x = i$
   $c = dp[j] + j^2 - S[j]$
   We can use the **Convex Hull Trick (CHT)** to maintain the lines and query the minimum at $x = i$. Since $i$ increases and slopes $-2j$ are monotonic, we can use a Deque for $O(N)$ inner DP.

3. **Algorithm:**
   Binary search $\lambda$ in range $[-10^{18}, 10^{18}]$.
   Inside check, run $O(N)$ DP using CHT (deque).
   Recover answer.

Complexity: $O(N \log (\text{Range of } \lambda))$.

\end{document}
