\documentclass[11pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{verbatim}

\geometry{letterpaper, margin=1in}

\title{\textbf{Problem D: The Aquarium}}
\author{Time Limit: 2.0s | Memory Limit: 256MB}
\date{}

\begin{document}

\maketitle

\section*{Description}

"I want to see everything... but I want to see it with you."

Touko Nanami and Yuu Koito are visiting the Aquarium. The aquarium is laid out as a long corridor with $N$ distinct exhibits, numbered $1$ to $N$. Each exhibit $i$ has a "Crowd Level" $A_i$.

Touko wants to plan a perfect date consisting of exactly $K$ **Moments**.
A "Moment" consists of walking through a contiguous range of exhibits $[L, R]$ without stopping.
The entire aquarium (exhibits $1$ to $N$) must be covered by these $K$ moments. That is, the indices $1$ to $N$ must be partitioned into exactly $K$ contiguous subarrays.

The **Mental Fatigue** of experiencing a single moment $[L, R]$ is calculated as:
$$ \text{Cost}(L, R) = (R - L + 1)^2 + \sum_{i=L}^{R} A_i $$
(The square of the length of the walk plus the sum of the crowd levels).

Touko wants to minimize the **Total Mental Fatigue**, which is the sum of the costs of the $K$ moments.

\section*{Input}

The first line contains two integers $N$ and $K$ ($1 \le K \le N \le 10^5$).
The second line contains $N$ integers $A_1, A_2, \dots, A_N$ ($1 \le A_i \le 10^9$).

\section*{Output}

Output a single integer: the minimum Total Mental Fatigue required to partition the aquarium into exactly $K$ moments.

\section*{Examples}

\subsection*{Example 1}
\textbf{Input:}
\begin{verbatim}
5 2
1 2 3 4 5
\end{verbatim}

\textbf{Output:}
\begin{verbatim}
28
\end{verbatim}

\textbf{Explanation:}
We need to split the array $[1, 2, 3, 4, 5]$ into 2 parts.
The optimal split is $[1, 2]$ and $[3, 4, 5]$ (or $[1, 2, 3]$ and $[4, 5]$).
Cost 1: $2^2 + (1+2) = 4 + 3 = 7$.
Cost 2: $3^2 + (3+4+5) = 9 + 12 = 21$.
Total: $7 + 21 = 28$.

\end{document}
